Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra

### 2018-10-07 manuscript/manuscript.tex
Evan suggestions.

In contrast, the beta coalescent generates $\hilopmi$ that is consistently greater than the constant-$N$ Kingman.
As with non-recombining sites, the $\hilopmi$ is also greater in the beta coalescent model than in models of population growth than generate similar distortions in the SFS.
This is true across recombination rates and high/low cutoff minor allele counts.

>>>>

In contrast, the beta coalescent generates $\hilopmi$ that is consistently greater than the constant-$N$ Kingman.
As with non-recombining sites, the $\hilopmi$ is also greater in the beta coalescent model than in models of population growth that generate similar distortions in the SFS.
This is true across recombination rates and high/low cutoff minor allele counts.
